---
title: "Pricing-Intangibles"
output: md_document
date: "2024-06-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("TestPlots.R")
#source("AdditionalData.R")
source("TestTables.R")
```

## Pricing-Intangibles

To Do:

Download LIQ Factor

[ ] Write 'ReadMe's' for every auxiliary File

Find out how to produce them with plots (-> maybe straight KNitR them?)

Do the LIQ ~ F_INT, & LIQ ~ FF regressions

Fucking get behind how to fix this fucking shit of a whore piece of git connection without suing github desktop those bunch of motherless sloths. die -> did it (will keep this as a memento tho)

Show the difference of the Factors when RMW is divided by be, or by be_int

MY BROTHER IN CHRIST: we forgot about the market factor. (did we?) -> check this straight after coming back from the doc!

#List of test plots:

[x] All the recreated fama french factors with the originals.

[x] All the intangible factors with the recreated fff.

[x] The two different rmw_int factors

([x] The different HML Factors)

[x] The Traded Liquidity Factor


#List of all the test tables:

[ ] All the recreated factors with the originals

[ ] Liq ~ FF5 OG

[ ] Liq ~ FF5 Int


#List of all factors and their composition:

[] All the original FF5

[] All the Int FF5 recreated

[] HML original and RMW Original

[] The Liquidity Factor


## Reproduction of Factors
```{r smb_reproduction, echo=FALSE }
smb.rep_plot

```




```{r hml_reproduction, echo=FALSE }
hml.rep_plot

```
```{r rmw_reproduction, echo=FALSE }
rmw.rep_plot

```

```{r cma_reproduction, echo=FALSE }
cma.rep_plot

```

```{r reproduction, message = FALSE, results = 'asis', echo = FALSE}
library(stargazer)
stargazer(model_smb, model_hml, model_rmw, model_cma, 
          type = "html",
          title = "Regressions of Replicated- onto Published Factors",
          colnames = FALSE,
          model.numbers = FALSE,
          dep.var.caption = "Factors from K. French's Website",
          dep.var.labels = c("SMB", "HML", "RMW", "CMA"),
          covariate.labels = c("SMB", "HML", "RMW", "CMA"),
          notes.align = "l")
```










## The intangible Factors


```{r hml_factor, echo=FALSE }
hml.fs_plot 

```

```{r hml_int, echo=FALSE }
hml.int_plot 

```





```{r rmw_factor, echo=FALSE }
rmw.fs_plot 

```

```{r rmw_OLD, echo=FALSE }
rmw.OLD_plot 

```




```{r cma_factor, echo=FALSE }
cma.fs_plot 

```




# The Liquidity "factor"

```{r liq_factor, echo=FALSE }
liq.f_plot 

```


```{r liq_measures, echo=FALSE }
liq.ms_plot

```


