---
title: "Pricing-Intangibles"
output: md_document
date: "2024-06-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("TestPlots.R")
source("AdditionalData.R")
source("TestTables.R")
```

## Pricing-Intangibles

To Do:

Download LIQ Factor

[ ] Write 'ReadMe's' for every auxiliary File

Find out how to produce them with plots (-> maybe straight KNitR them?)

Do the LIQ ~ F_INT, & LIQ ~ FF regressions

Fucking get behind how to fix this fucking shit of a whore piece of git connection without suing github desktop those bunch of motherless sloths. die -> did it (will keep this as a memento tho)

Show the difference of the Factors when RMW is divided by be, or by be_int

MY BROTHER IN CHRIST: we forgot about the market factor. (did we?) -> check this straight after coming back from the doc!

List of test plots:

[ ] All the recreated fama french factors with the originals.

[ ] All the intangible factors with the recreated fff.

[ ] The two different rmw_int factors

([ ] The different HML Factors)

[ ] The Traded Liquidity Factor

List of all the test tables:

[ ] All the recreated factors with the originals
[ ] Liq ~ FF5 OG
[ ] Liq ~ FF5 Int


List of all factors and their composition:

[ ] All the original FF5
[ ] All the Int FF5 recreated
[ ] HML original and RMW Original
[ ] The Liquidity Factor


```{r cars}
summary(cars)
```

##Plots


```{r hml_reproduction, echo=FALSE, out.height= "50%" }
hml_plot

```


## Tables 
```{r reproduction, message = FALSE, results = 'asis', echo = FALSE}
library(stargazer)
stargazer(model_smb, model_hml, model_rmw, model_cma, type = "html")
```


